\vspace{-2.25cm} Multimodal Abnormity-Aware Model\\for Ocular Disease Diagnosis

### 2024-08-29 Paper/Paper.tex
add model_overview.png
plot combined acc; continue writing training section

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=\linewidth]{Figs/Temp.png}
		\caption{Model Overview}
		\vspace{0.3cm}
		\label{fig:3_parts}
	\end{figure}

@@

	Then, for OCT abnormities with less than 1000 images, we use Cycle-GAN to generate new images. We train a Cycle-GAN network to interconvert healthy and abnormity images, take out the generator that converts healthy to abnormity images, and use it to generate new abnormity images. We manually eliminate generated images that look obviously wrong. The elimination rates are shown in Table~\ref{tb:cycleGAN_number}. We did not use Cycle-GAN to generate fundus images because generated fundus images are too blurry and do not display the desired abnormities.

	{
		\fontsize{9}{12}\selectfont
		{
			\begin{longtable}{ccccc}
				\caption{OCT images CycleGAN elimination rates}
				\label{tb:cycleGAN_number}\\
				\toprule
				Abnormity&Original&Generated&Eliminated&Elimination Rate\\
				\midrule
				CSC   &134&3000&1270&42.333\% \\
				ERM   &19 &3000&1069&35.633\% \\
				MH    &130&3000&1189&39.633\% \\
				Mactel&29 &3000&1100&36.667\% \\
				RP    &133&3000&1077&36.900\% \\
				ST    &23 &3000&418 &13.933\% \\
				\bottomrule
			\end{longtable}
		}
	}

	We separate the images, including generated images, into training and testing datasets. We implement a set of transformations on the images, including horizontal flips, random brightness changes from -10\% to +10\%, random horizontal and vertical translations between -5\% and +5\%, random scaling between -20\% and +20\%, and random rotations, which are between -10$^\circ$ and +10$^\circ$ for OCT images and between -30$^\circ$ and +30$^\circ$ for fundus images. The rotation is only applied to images in the train dataset. Eventually, we get 5000 train images and 500 test images for each OCT abnormity, and 3000 train images and 300 test images for each fundus abnormity.

@@

	For both OCT and Fundus Models, we employ a strategy of transfer learning to finetuning.

	In the transfer learning phase, we use pretrained weights from ImageNet. We freeze the weights in all the convolutional layers and only allow the weights in the final FC layer to learn. We train the model for 100 epochs. Every 10 epochs, we save the weights of the model with the best validation accuracy. Of all the saved models, we find the model with the best overall performance on the validation and testing datasets, and start finetuning based on this model.

	In the finetuning phase, we start on the best model in the transfer learning phase, unfreezing all weights in the model. We train the model for 30 epochs. Similarly, we save the weights of the model with the best validation accuracy every 10 epochs, and find the model with the best overall performance. Finally, we compare the performance of the best model in the transfer learning phase and the best one in the finetuning phase to determine the final model.

	For OCT

	The accuracies and losses during training and validation phases are shown in Fig.~\ref{fig:AO_train} and Fig.~\ref{fig:AF_train}.

@@

	Graph bar chart for comparison?

>>>>

	\begin{figure}[htbp]
		\centering
		\includegraphics[width=\linewidth]{Figs/model_overview.png}
		\caption{Model Overview}
		\vspace{0.3cm}
		\label{fig:3_parts}
	\end{figure}

@@

	Then, for OCT abnormities with less than 1000 images, we use Cycle-GAN to generate new images. We train a Cycle-GAN network to interconvert healthy and abnormity images, take out the generator that converts healthy to abnormity images, and use it to generate new abnormity images. We go through all generated images and adopt those that clearly display only the desired abnormities. The adoption rates are shown in Table~\ref{tb:cycleGAN_number}. We did not use Cycle-GAN to generate fundus images because generated fundus images are too blurry and do not show the desired abnormities.

	{
		\fontsize{9}{12}\selectfont
		{
			\begin{longtable}{ccccc}
				\caption{OCT images CycleGAN adoption rates}
				\label{tb:cycleGAN_number}\\
				\toprule
				Abnormity&Original&Generated&Adopted&Adoption Rate\\
				\midrule
				CSC   &134&3000&1730&58.667\% \\
				ERM   &19 &3000&1931&64.367\% \\
				MH    &130&3000&1811&60.367\% \\
				Mactel&29 &3000&1900&63.333\% \\
				RP    &133&3000&1923&63.100\% \\
				ST    &23 &3000&2572&86.067\% \\
				\bottomrule
			\end{longtable}
		}
	}

	We separate the images, including generated images, into training and test datasets. We implement a set of transformations on the images, including horizontal flips, random brightness changes from -10\% to +10\%, random horizontal and vertical translations between -5\% and +5\%, random scaling between -20\% and +20\%, and random rotations, which are between -10$^\circ$ and +10$^\circ$ for OCT images and between -30$^\circ$ and +30$^\circ$ for fundus images. The rotation is only applied to images in the train dataset. Eventually, we get 5000 train images and 500 test images for each OCT abnormity, and 3000 train images and 300 test images for each fundus abnormity.

@@

	For the Abnormity Models, we employ a strategy of transfer learning to finetuning.

	In the transfer learning phase, we use pretrained weights from ImageNet. We freeze the weights in all the convolutional layers and only allow the weights in the final FC layer to learn. We train the model for 100 epochs. Every 10 epochs, we save the weights of the model with the best validation accuracy. For all the saved models, we calculate a overall accuracy, which is the weighted average of validation and test accuracy, to find the model with the best overall performance on the validation and test datasets, and start finetuning based on this model.

	In the finetuning phase, we start on the best model in the transfer learning phase, unfreezing all weights in the model. We train the model for 30 epochs. Similarly, we save the weights of the model with the best validation accuracy every 10 epochs, and find the model with the highest overall accuracy. Finally, we compare the overall accuracies of the best model in the transfer learning phase and the finetuning phase to determine the final model.

	For both OCT and Fundus Models, we trained 4 commonly used CNNs: ResNet152, ResNet50, ResNet18, and VGG16. The accuracies and losses during training and validation phases are shown in Fig.~\ref{fig:AO_train} and Fig.~\ref{fig:AF_train} for all of the CNNs.

@@

	{
		\fontsize{9}{12}\selectfont
		{
			\begin{table}
				\centering
				\caption{Validation accuracies}
				\label{tb:A_accuracies}
				\begin{tabular}{ccccc}
					\toprule
					Model&ResNet152&ResNet50&ResNet18&VGG16\\
					\midrule
					OCT Model   &91.906\%&\textbf{92.183\%}&91.011\%&89.744\% \\
					Fundus Model&\textbf{89.111\%}&88.926\%&86.605\%&79.185\% \\
					\bottomrule
				\end{tabular}
			\end{table}
		}
	}
